\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.48\textwidth]{figures/f-plain.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-plain.pdf}\\
        \vspace{-0.8cm}
        \includegraphics[width=0.48\textwidth]{figures/f-adversary.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-adversary.pdf}
    \end{center}
    \vspace{-1cm}
    \caption{Toy example.
    (Upper left) Conditional probability densities of the decision scores for $Z=0, 1, 2$
       when $f$ is built without adversarial training. The resulting densities
       are clearly dependent on $Z$, indicating that $f$ is not pivotal.
    (Upper right) The corresponding decision surface, highlighting
       the fact that samples are easier to classify for values of $Z$ closer to $2$,
       hence partially explaining the dependency.
    (Lower left) Conditional probability densities of the decision scores for $Z=0, 1, 2$ when $f$ is
       built with adversarial training, as outlined in Section~\ref{sec:method}.
       The resulting densities are now almost identical to each other, indicating only a
       small dependency on $Z$.
    (Lower right) The corresponding decision surface, illustrating how adversarial
       training bends the decision function to erase the dependency on $Z$.
    }
    \label{fig:toy}
\end{figure*}

\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/training.pdf}
    \vspace{-1cm}
    \caption{Toy example. Training curves for ${\cal L}_f(\theta_f)$, ${\cal L}_r(\theta_f, \theta_r)$
             and ${\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r)$.
             Adversarial training was performed for $75$ iterations, mini-batches of size $M=128$, $K=100$ and $\lambda=50$.}
    \label{fig:toy-training}
\end{figure}

>>>>

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.48\textwidth]{figures/f-plain.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-plain.pdf}\\
        \vspace{-0.8cm}
        \includegraphics[width=0.48\textwidth]{figures/f-adversary.pdf}
        \includegraphics[width=0.48\textwidth]{figures/surface-adversary.pdf}
    \end{center}
    \vspace{-1cm}
    \caption{Toy example.
    (Upper left) Conditional probability densities of the decision scores for $Z=0, 1, 2$
       when $f$ is built without adversarial training. The resulting densities
       are clearly dependent on $Z$, indicating that $f$ is not pivotal.
    (Upper right) The corresponding decision surface, highlighting
       the fact that samples are easier to classify for values of $Z$ closer to $2$,
       hence partially explaining the dependency.
    (Lower left) Conditional probability densities of the decision scores for $Z=0, 1, 2$ when $f$ is
       built with adversarial training, as outlined in Section~\ref{sec:method}.
       The resulting densities are now almost identical to each other, indicating only a
       small dependency on $Z$.
    (Lower right) The corresponding decision surface, illustrating how adversarial
       training bends the decision function vertically to erase the dependency on $Z$.
    }
    \label{fig:toy}
\end{figure*}

\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/training.pdf}
    \vspace{-1cm}
    \caption{Toy example. Training curves for ${\cal L}_f(\theta_f)$, ${\cal L}_r(\theta_f, \theta_r)$
             and ${\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r)$.
             Adversarial training was performed for $100$ iterations, mini-batches of size $M=128$, $K=100$ and $\lambda=50$.}
    \label{fig:toy-training}
\end{figure}
